Full Title

### 2022-03-07 README.Rmd
customize templates

# Research Compendium Template

This is a research compendium template geared towards producing a manuscript output as a Word document reproducibly using the `targets` package for workflow management.
See the [`targets` documentation](https://docs.ropensci.org/targets/) for more information on how to program analyses in this style.
I've found that writing `paper.Rmd` using RStudio's [visual markdown editor](https://rstudio.github.io/visual-markdown-editing/) and automatic text wrapping (with each sentence as a new line) works best for version control and collaboration with git and GitHub.
The visual editor also integrates seamlessly with [Zotero](https://www.zotero.org/) for adding in-text citations and bibliographies.
The [`renv` package](https://rstudio.github.io/renv/articles/renv.html) my also be useful for collaboration to keep package version synced across collaborators.
Before submitting the manuscript, I like to [archive my GitHub repository with Zenodo](https://guides.github.com/activities/citable-code/) and add a DOI badge to the README, and a link to the Zenodo archive to the Data Availability Statement.
In the `review` directory, you'll find my preferred way of structuring response to reviewers complete with the ability to cross-reference responses to avoid repeating yourself.

**GithHub Actions** This template also uses [GitHub actions](https://github.com/features/actions) to automatically render a .html version of the manuscript every time an edit to docs/paper.Rmd is made.
If [GitHub pages](https://pages.github.com/) are active, then the rendered draft is viewable at \<username\>.github.io/\<repository name\>/paper.html.
The workflow for this lives in .github/workflows/build-manuscript.yaml and can be disabled on GitHub in the "Actions" tab.

Readme text for *your* repository below:

------------------------------------------------------------------------

@@

This repository contains data and code for a manuscript by \_\_\_\_\_\_ written for submission to \_\_\_\_\_\_ tentatively titled: \_\_\_\_\_.

The most recent draft of the manuscript is available [here](https://aariq.github.io/paper-template/paper.html).

@@

Additional instructions if project uses `targets`:

-   Install the [`targets` package](https://docs.ropensci.org/targets/).
-   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs.

**NOTE**: the GitHub actions in .github/workflows/build-manuscript.yaml will not work with a `targets` project.
Consider `targets::tar_github_actions()` as an alternative

>>>>

@@

This repository contains data and code for a manuscript by Eric Scott and Emilio Bruna written for submission to The American Naturalist tentatively titled: \_\_\_\_\_.

The most recent draft of the manuscript is available [here](https://brunalab.github.io/lagged-ipms/paper.html).

@@

<!-- Additional instructions if project uses `targets`: -->

<!-- -   Install the [`targets` package](https://docs.ropensci.org/targets/). -->

<!-- -   Run `targets::tar_make()` or `targets::tar_make_clustermq()` from the R console to run all code and produce all outputs. -->

<!-- **NOTE**: the GitHub actions in .github/workflows/build-manuscript.yaml will not work with a `targets` project. -->

<!-- Consider `targets::tar_github_actions()` as an alternative -->

### 2022-03-07 docs/paper.Rmd
customize templates

---
title: "Full Title"
shorttitle: "Running Title"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Co-author two:
      email: secondperson@university.edu
      institute: [affiliation2]
      correspondence: false
  - Co-author three:
      email: thirdperson@university.edu
      institute: [UF_WEC, affiliation2]
      correspondence: false

institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - affiliation2: Department of Ecology, Evolution and Environmental Biology, Example University 123 Center Avenue, New York, New York 10027 USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      #- -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/global-change-biology.csl" # Insert path for the bib-style
keywords: |
  keyword1; keyword2; keyword3
highlights: |
  These are the highlights

>>>>

---
title: "Full Title"
shorttitle: "Running Title"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

institute:
  - UF_WEC: Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida 32611-0430
  - UF_LAS: Center for Latin American Studies, University of Florida, Gainesville, Florida 32611-5530  
  - BDFFP: Biological Dynamics of Forest Fragments Project, INPA-PDBFF, CP 478, Manaus, Amazonas 69011-970 Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      linenumbers: yes
      number_sections: no
      fig_caption: yes
      reference_docx: "templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=templates/scholarly-metadata.lua
      - --lua-filter=templates/author-info-blocks.lua
      #- -Fpandoc-crossref #required for cross-ref equations
linkcolor: blue
bibliography: references.bib
csl: "templates/the-american-naturalist.csl" # Insert path for the bib-style
keywords: |
  keyword1; keyword2; keyword3
highlights: |
  These are the highlights
